\input{include.tex}
\begin{document}

\begin{minipage}{0.7\linewidth}
\textbf{Nicolas Silva} ~\\
12 rue Romarin ~\\
69001, Lyon (France)~\\
\url{nicolas.silva@insa-lyon.fr} ~\\
(+33)6 42 02 48 37
\end{minipage}

\begin{minipage}{0.2\linewidth}
Student ~\\
French nationality ~\\

\end{minipage}


\section*{Career plan}
	\begin{itemize}
		\item
	\end{itemize}
\section*{Education}
	\begin{itemize}
		\item{2009-10} $3^{rd}$ year at INSA de Lyon Engineering School IT and Computer Science Department INSA 
		\item{2008-09} $2^{nd}$ year in International Section. Lectures in English. INSA
		\item{2007-08} $1^{st}$ year, general scientific knowledge – Physics, math, mechanics, chemistry...
		\item{2007}: Scientific High School Diploma with Honors.
	\end{itemize}
\section*{Computer ccience skills}
	\begin{itemize}
		\item Programmation langages: C, C++, Java, Python, Pascal, Matlab, Maple, \LaTeX, \texttt{Asm 68k}, xhtml, css, MySQL, Oracle SQL. 
		\item software libraries: \{c++: OpenGL, OpenCL\}, \{java: TopLink\}.
		\item collaborative methods & platforms: Agile method, UML, Merise, SVN, Mercurial. 
		\item softwares: Eclipse, Netbeans, The Gimp, InkScape, Blender, Photoshop.
	\end{itemize}
\section*{Languages}
	\begin{itemize}
		\item{Anglais:} Fluent. 1 year in the bilingual section of the INSA (all lectures in english), 7 weeks in Australia as a Student exchange.
		\item{Espagnol:} read, writen, spoken. 4 weeks in Argentina.
	\end{itemize}
\section*{Work experiences & associative involvment}
	\begin{itemize}
		\item{June 2007: } 1 month internship at VG Goossens in Meyzieu (France).
		\item{2008 - 2009:} \textbf{Graphiste} pour l'association étudiante INSA Game Creator.
		\item{2009 - 2010:} \textbf{Illustrateur} au journal étudiant l'Insatiable.
		\item{2009 - 2010:} Organisateur du Gala de l'INSA de Lyon.
	\end{itemize}
\section*{Interests & activities}
	\begin{itemize}
		\item{Music:} Piano & chant dans un groupe.
		\item{Graphic arts, Drawing, infography}.
		\item{Programmation} 3D (\texttt{C++/OpenGL}).
		\item Ski, Natation.
	\end{itemize}


\end{document}
