\input{./include.tex}
\begin{document}


\begin{minipage}{0.6\textwidth}
\flushleft{
\textbf{Nicolas Silva} ~\\
12 rue Romarin ~\\
69001, Lyon (France)~\\
(+33)6 42 02 48 37\\
\url{nicolas.silva@insa-lyon.fr} ~\\
\url{https://github.com/nical/}
}
\end{minipage}

\begin{minipage}{0.35\textwidth}
\flushright{
 ~\\Student
 ~\\French nationality
}
\end{minipage}



\section*{Career plan}
Software architect in creativity oriented software development.

\section*{Education}
	\begin{itemize}
		\item{2009-11} $3^{rd}$ and $4^{rd}$ years at INSA Lyon School of engineering, IT and Computer Science Department.
		\item{2008-09} $2^{nd}$ year in International Section.All courses \textbf{in English}. INSA
		\item{2007-08} $1^{st}$ year, general scientific knowledge. INSA
		\item{2007}: Scientific High School Degree, graduated with Honours.
	\end{itemize}
\section*{Skills}
	\begin{itemize}
		\item Programming langages: C, C++, D, Java, Python, \LaTeX, \texttt{Asm 68k}, xhtml, css, SQL, Prolog. 
		\item Software libraries: {\color{gray}\{c++:} Qt, Boost, OpenGL, VtK, Cairo {\color{gray}\} }, {\color{gray}\{java: } TopLink, Swing {\color{gray}\}}.
		\item Network programming, real-time programming, multi-task programming.
		\item Collaborative methods \& platforms: Agile method, USDP, UML, Merise, Git, Mercurial, SVN.
		\item Project management, software quality
	\end{itemize}
\section*{Languages}
	\begin{itemize}
		\item{French:} Native language.
		\item{English:} Fluent. 1 year in the bilingual section of the INSA (all lectures in english), 7 weeks in Australia as an exchange student.
		\item{Spanish:} read, writen, spoken. 4 weeks in Argentina.
	\end{itemize}
\section*{Work experiences}
	\begin{tabbing}
		~~~~~~~~~~~~~~~~~~~~~~~\= ~~\= \kill
		June 2007 \> Internship at VG Goossens (France) as a factory worker.\\
		1 month\\
		summer 2010 \> Internship at Liris (Computer Science Laboratory, Imagery department) \\ 3 months \> {\footnotesize \color{gray}[C++/Python]} ParaView plugin optimzation \& developement of a plugin source code generator.\\
		\> {\footnotesize \color{gray}[C++]} Development of an optimsed data structure based on Morton hash-tree.
	\end{tabbing}
\section*{Associative involvements }
	\begin{itemize}
	
		\item{2010 - 2011:} \textbf{Graphist} for the student union (annual budget: 500k€).
		\item{2009 - 2010:} \textbf{Graphist} for the student new paper \textit{l'Insatiable}.
		\item{2009 - 2010:} Organizer of the INSA Lyon Gala, decoration team (budget 180k€).
		\item{2008 - 2009:} \textbf{Graphist} for the student club INSA Game Creator.
	\end{itemize}
\section*{Interests \& activities }
	\begin{itemize}
		\item{Music:} Piano, guitar.
		\item{Graphic arts, Drawing, Painting, infography}.
		\item{Programming} (\texttt{C++/D/OpenGL/Cairo/Qt}). ~\\
			Developement of an open-source generic node compositor library in \texttt{C++} {\footnotesize(\url{https://github.com/nical/kiwi})}.
		\item Ski, Natation.
	\end{itemize}


\end{document}
